Crossing Origins by Crossing Formats

### 2012-12-03 main.tex
Section 4 Evaluation

@@

@@

Vulnerable: Firefox, Safari, Opera, Chrome

Not vulnerable: Internet Explorer

\todo{see if this makes sense here}
As it turns out, various browser plug-ins deal with the situation differently. The Chrome browser
built-in PDF reader refuses to render content that was served with an inappropriate 
MIME-type. If the 
Chrome browser is configured to use the Adobe Reader plug-in, the behavior will 
be the same as in other browsers and the content will be interpreted as PDF.
The Java plug-in used to ignore the MIME-type, but after several 
vulnerabilities were disclosed, this behavior was changed.

Vulnerable: Adobe Reader

Not vulnerable: Chrome PDF-viewer

Not tested: Apple Preview

\subsection{Bypassing content filters}

\subsubsection{Server-side upload filters}

Filter can verify that the benign file format is indeed benign without ever
noticing the malicious file format hidden within.

\subsubsection{Cross-site scripting filters}

This effectively bypasses any cross-site scripting filters such as NoScript or
filters built into browsers. Since the Reader plug-in handles the response, the
browser never gets to see the content

\subsubsection{Context sensitive filters}

Clever filters that adapt their filtering to the context in which the user
content is included. Basically filters that allow input that do not form harmfulHTML.

>>>>

This section details the evaluation performed to investigate the persistence of 
the vulnerabilities from Section~\ref{sec:vuln}. The evaluation covers various 
instances of affected components, such as browsers and PDF interpreters, 
content sanitization filter, and a study of the Alexa top 100 websites.

@@

Section~\ref{sec:vuln} focus on the Adobe PDF Reader as the attack surface, 
due to its standing as the most commonly used reader. To give a comparison, the 
Google Chrome built-in PDF reader, was selected as it is the default reader to 
user of the browser.

As mentioned in Section~\ref{sec:cross}, the browser rely on the reader plug-in to 
implement correct security measures, in order to prevent cross-domain leakage. 
Unlike Adobe Reader, the Chrome browser built-in PDF reader refuses to render 
content that was served with an inappropriate MIME-type if the content is 
delivered across origins. This effectively prevents the attacks in Section~\ref{sec:vuln}.
If the Chrome browser is configured to use the Adobe Reader plug-in, it will 
behave the same as in other browsers and the content will be interpreted as PDF.

@@

The behavior of cross-domain embedding of PDF resources is studied in the major 
browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
The study shows that all major browsers are susceptible to the attacks outlined 
in Section~\ref{sec:vuln}, with some minor differences.

\paragraph{Safari and Opera}
The browsers, Safari and Opera, are both susceptible to the attacks outlined as 
per Section~\ref{sec:vuln}, without any restrictions or modifications.

\paragraph{Firefox}
The Mozilla Firefox browser is susceptible to the attacks, with the restriction 
that the PostMessage API is unavailable. This merely prevents one channel of 
communication with the attacker, and does not reduce the threat.

\paragraph{Internet Explorer}
Microsoft's browser, Internet Explorer, is susceptible to the attacks. However, 
it seems to only support embedding of PDF documents using the \emph{embed} tag. 
This is not a major obstacle in exploiting the vulnerability, as the embed and 
object tags are interchangeable in this respect.

\paragraph{Google Chrome}
Google's browser, Chrome, has built-in support for displaying PDF documents. 
The built-in PDF reader is used by default by the browser, unless it has been 
explicitly disabled by the user. Certain complex PDF documents can not be 
handled by the built-in reader. The built-in reader will then prompt the user 
to open the document in Adobe Reader. As previously noted, the built-in reader 
is not vulnerable to attacks. Hence, Chrome is only susceptible when the Adobe 
Reader plug-in is used to render the document.

%\subsection{Bypassing content filters}

%\subsubsection{Server-side upload filters}

%As discussed in Section~\ref{sec:cross} server-side content filters that 
%validate files based on content type are not equipped to handle polyglot 
%content. For polyglot content, specialized filters are required that analyze 
%the content based on all considerable interpretations of the content. No such 
%filters were encountered in this study.

%\subsubsection{Cross-site scripting filters}
%\todo{install NoScript?}
%This effectively bypasses any cross-site scripting filters such as NoScript or
%filters built into browsers. Since the Reader plug-in handles the response, the
%browser never gets to see the content

%\subsubsection{Context sensitive filters}

%Context sensitive cross-site scripting filters, that remove or encode characters
%Clever filters that adapt their filtering to the context in which the user
%content is included. Basically filters that allow input that do not form harmfulHTML.

% Don't want to claim something I have no basis for..
